---
title: "Writing Functions"
output: github_document
---

```{r setting up R markdown}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis", 
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Do Something Simple 

```{r}
x_vec = rnorm(30, mean = 5, sd = 3)

(x_vec - mean(x_vec)) / sd(x_vec)
#Z scores, SD away from the mean
```

I want a function to compute z scores 

```{r}
z_scores = function(x) {
  
  if(!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if(length(x) < 3) {
    stop("Inpute must have at least 3 numbers")
  }
  
  z = (x - mean(x)) / sd(x)
  
  return(z)
}

z_scores(x_vec)
```

Try function on other things. These should give errors. 

```{r error = TRUE}
z_scores(3)
#Sd of 3 can't do
#can't do mean on character var 
z_scores(mtcars)
#can't take mena of dataset, only number list
z_scores(c(TRUE, TRUE, FALSE, TRUE))
#coerced to 0 and 1

```

## Multiple Outputs

```{r}
mean_and_sd = function(x) {
  
  if(!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if(length(x) < 3) {
    stop("Inpute must have at least 3 numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

Check that function worked

```{r}
x_vec = rnorm(100, mean = 3, sd = 4)
mean_and_sd(x_vec)
```

## Multiple inputs 

Give me a sample size, mean, sd

```{r}
sim_data = 
  tibble(
    x = rnorm(n = 100, mean = 4, sd = 3)
  )

#create dataframe
sim_data %>% 
  summarise(
    mean = mean(x),
    sd = sd(x)
  )
#get mean and sd
```

I'd like to do this with a function

```{r}
sim_mean_sd = function(samp_size, mu = 3, sigma = 3) {
  
  sim_data = 
  tibble(
    x = rnorm(n = samp_size, mean = mu, sd = sigma)
  )

sim_data %>% 
  summarise(
    mean = mean(x),
    sd = sd(x)
  )
  
}

sim_mean_sd(samp_size = 100, mu = 6, sigma = 3)

sim_mean_sd(samp_size = 100, sigma = 3)
sim_mean_sd(samp_size = 100)
```

## Lets review Napoleon Dynamite 

Scraping reviews from Napoleon Dynamite

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

#extract elements of data we're interested in - ID css tag
#Selector gadget
#Convert to text

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  #get first digit number between 0-9 at start of string input 
  as.numeric()
#convert from char to numeric = review stars

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews_page1 = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
#put reviews into tibble
```

What about next page of reviews?

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

#extract elements of data we're interested in - ID css tag
#Selector gadget
#Convert to text

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  #get first digit number between 0-9 at start of string input 
  as.numeric()
#convert from char to numeric = review stars

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews_page2 = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
#put reviews into tibble
```

Don't want to just copy and paste. There are several pages of reviews (1800 reviews). 

Turn into function. Input, read URL for that page of reviews.

```{r}

read_page_reviews <- function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}

```

Let's try the function

```{r}
dyn_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=3"

read_page_reviews(dyn_url)

```

Read a few pages of reviews 

```{r}
dyn_url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

dyn_urls = str_c(dyn_url_base, 1:5)

dyn_urls[3]

all_reviews = 
  bind_rows(
    read_page_reviews(dyn_urls[1]),
    read_page_reviews(dyn_urls[2]),
    read_page_reviews(dyn_urls[3]),
    read_page_reviews(dyn_urls[4]),
    read_page_reviews(dyn_urls[5])
  )

all_reviews
```

If we wanted 50 pages of reviews, would prefer not to have this code 50 times.
